--- 
title: "Ravelry in Review"
author: "Alex McSween"
format: 
  dashboard:
    logo: images/logo.png
    nav-buttons: 
     - icon: github
       href: https://github.com/alexmcsw/ravelry-in-review
     - icon: activity
       href: https://www.ravelry.com/people/amcsw
    theme: 
        light: minty
---

```{r}
#| include: false
library(jsonlite)
library(purrr)
library(dplyr)
library(ggplot2)
library(ggimage)
library(gt)
library(stringr)
library(tidyr)
library(zoo)
lapply(
  list.files("./functions/", full.names = TRUE),
  source
)

path <- "./data/json/projects/"
files <- dir(path, pattern = "*.json")

df <- data.frame()

for (file in files) {

  temp <- paste0(path,file) %>%
    fromJSON() %>%
    unlist() %>%
    as.matrix() %>%
    t() %>%
    as.data.frame()

  df <- dplyr::bind_rows(df, temp)
}

palette <- c(
  "#6610f2",
  "#007bff",
  "#78c2ad",
  "#6f42c1",
  "#e83e8c",
  "#20c997",
  "#ffce67",
  "#56cc9d",
  "#ff7851",
  "#6cc3d5",
  "#fd7e14",
  "#f3969a"
)

set.seed(Sys.Date())


```

# All-time
```{r}

open_projects <- df |> filter(status_name == "In progress") |> count() |> as.numeric()

completed_projects <- df |> filter(status_name == "Finished") |> count() |> as.numeric()

gift_projects <- df |> filter(!(made_for %in% c("me", "Me", "me!", "ME", "", NA))) |> count() |> as.numeric()

me_projects <- df |> filter((made_for %in% c("me", "Me", "me!", "ME", "", NA))) |> count() |> as.numeric()

meterage <<- df |>
  select(contains("packs.total_meters")) |>
  mutate(across(everything(), as.numeric)) |>
  sum(na.rm = TRUE) |>
  as.numeric() / 1000

```
## Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Completed Projects"

list(
  icon = "check-all",
  color = "secondary",
  value = completed_projects
)
```

```{r}
#| content: valuebox
#| title: "Active WIPs"

list(
  icon = "cone-striped",
  color = "#ffce67",
  value = open_projects
)
```

```{r}
#| content: valuebox
#| title: "Kilometers knitted"

list(
  icon = "rulers",
  color = "light",
  value = meterage |> round(digits = 2)
)
```

```{r}
#| content: valuebox
#| title: "Gifts made"

list(
  icon = "gift",
  color = "pink",
  value = gift_projects
)
```

## Row {height=70%}
### Column {width=25%}

```{r}

most_favourited <- df |> mutate(favorites_count = as.numeric(favorites_count)) |> filter(favorites_count == max(favorites_count)) |> slice_sample(n = 1)


images <- list.files(
    path = "data/photos/project",
    pattern = paste0(most_favourited |> select(permalink), "-\\d.jpg"),
    full.names = TRUE
)
```

```{r}
#| title: Most favourited project
#| padding: 0px
#| expandable: false


plot <- ggplot() + geom_image(aes(x = 1,  y= 1, image = sample(images, 1)), size = 0.7) + theme_void()

table <- most_favourited |> 
    select(name, favorites_count, links.self.href, comments_count) |>
    gt() |>
    fmt_url(
    columns = links.self.href,
    label = "Ravelry",
    show_underline = FALSE
  ) |>
    cols_add(heart = "Heart", comment = "comment") |>
    fmt_icon(heart, fill_color = "red", stroke_color = "red") |>
    fmt_icon(comment, fill_color = "blue", stroke_color = "blue") |>
    cols_merge(
        columns = c(name, links.self.href),
        pattern = "{1} ({2})"
    )  |>
    cols_merge(
        columns = c(favorites_count, heart, comments_count, comment),
        pattern = "{2} {1} {4} {3}"
    ) |>
    cols_width(name ~ pct(75), favorites_count ~ pct(25)) |>
    cols_label(name = "Project", favorites_count = "") |>
    opt_stylize(color = "pink") |>
    tab_options(
      table.width = pct(90),
      container.overflow.y = FALSE
    )
  


plot

table
  
```


### Column {width=75%}
```{r}
#| title: Knitting categories
#| padding: 4px
#| expandable: false

#define clothing categoryies
accessory <- "bag|purse|clutch|pouch"
cardigan <- "cardi"
hats <- "hat|toque|beanie|hood|balaclava|hue"
mitts <- "mitten|gloves"
scarf <- "scarf|shawl|collar"
shirt <- "tee|tank|polo|cami|top|shirt|blouse|bralette"
socks <- "socks|slippers|boots"
sweater <- "sweater|jumper|pullover"
vest <- "vest|slipover"

df_category <- df |> mutate(
  category = case_when(
    grepl(accessory, tolower(pattern_name)) ~ "Bags",
    grepl(cardigan, tolower(pattern_name)) ~ "Cardigans",
    grepl(hats, tolower(pattern_name)) ~ "Hats",
    grepl(mitts, tolower(pattern_name)) ~ "Mittens",
    grepl(scarf, tolower(pattern_name)) ~ "Scarves",
    grepl(shirt, tolower(pattern_name)) ~ "Tops",
    grepl(socks, tolower(pattern_name)) ~ "Socks",
    grepl(sweater, tolower(pattern_name)) ~ "Sweaters",
    grepl(vest, tolower(pattern_name)) ~ "Vests",
    .default = "Other"
  ),
  category = case_when(
    category == "Other" & grepl(accessory, tolower(name)) ~ "Bags",
    category == "Other" & grepl(cardigan, tolower(name)) ~ "Cardigans",
    category == "Other" & grepl(hats, tolower(name)) ~ "Hats",
    category == "Other" & grepl(mitts, tolower(name)) ~ "Mittens",
    category == "Other" & grepl(scarf, tolower(name)) ~ "Scarves",
    category == "Other" & grepl(shirt, tolower(name)) ~ "Tops",
    category == "Other" & grepl(socks, tolower(name)) ~ "Socks",
    category == "Other" & grepl(sweater, tolower(name)) ~ "Sweaters",
    category == "Other" & grepl(vest, tolower(name)) ~ "Vests",
    .default = category
),
# a bit of manual entry here
# lesson is to be more specific in my rav projects!!
category = case_when(
  grepl("tulip|delphinus|vair|cloudbow", tolower(name)) ~ "Sweaters",
  grepl("sulina|kostner|silvatica|snaraness|gossamer", tolower(name)) ~ "Scarves",
  grepl("springfrost|coaticook|reverie", tolower(name)) ~ "Socks",
  grepl("willapund", tolower(name)) ~ "Vests",
  grepl("llelua", tolower(name)) ~ "Hats",
  grepl("cyanotype", tolower(name)) ~ "Mittens",
  .default = category
)
) |>
select(completed, created_at, started, updated_at, category) |>
mutate(across(c(completed, created_at, started, updated_at), as.Date)) |>
mutate(
  started = case_when(
    is.na(started) ~ created_at,
    .default = started
  ),
  completed = case_when(
    is.na(completed) ~ updated_at,
    .default = completed
  ),
  .keep = "unused"
) |> filter(started < completed)
```

```{r}
#| title: Projects over time
#| #| padding: 4px
#| expandable: false
#| fig-width: 15
#| fig-height: 5

date_df <- data.frame(
  date = seq(min(df_category$started), max(df_category$completed), by = "days")
)

df_date <- df_category |>
  mutate(
    Date = map2(
      as.Date(started),
      as.Date(completed),
      seq,
      by = "1 day"
    ),
    Project = seq(nrow(df_category)),
    .keep = "unused"
  ) |>
unnest(cols = c(Date))



df_date |>
ggplot(aes(x=Date, after_stat(count), fill = category)) + 
geom_density(position = "stack", alpha = 0.5, colour = "white") +
scale_fill_manual(values = palette) +
theme_minimal()


```


# 2024
```{r}

make_value_boxes("2024")

```
## Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Completed Projects"

list(
  icon = "check-all",
  color = "secondary",
  value = completed_projects
)
```

```{r}
#| content: valuebox
#| title: "Projects started"

list(
  icon = "cone-striped",
  color = "#ffce67",
  value = started_projects
)
```

```{r}
#| content: valuebox
#| title: "Kilometers knitted"

list(
  icon = "rulers",
  color = "light",
  value = meterage |> round(digits = 2)
)
```

```{r}
#| content: valuebox
#| title: "Gifts made"

list(
  icon = "gift",
  color = "pink",
  value = gift_projects
)
```

## Row {height=70%}
### Column {width=25%}

```{r}
#| title: Most favourited project
#| padding: 0px
#| expandable: false

most_favourited <- df_year |> mutate(favorites_count = as.numeric(favorites_count)) |> filter(favorites_count == max(favorites_count)) |> slice_sample(n = 1)


images <- list.files(
    path = "data/photos/project",
    pattern = paste0(most_favourited |> select(permalink), "-\\d.jpg"),
    full.names = TRUE
)

plot <- ggplot() + geom_image(aes(x = 1,  y= 1, image = sample(images, 1)), size = 0.7) + theme_void()

table <- make_table(most_favourited)
  

plot
table
  
```


### Column {width=35%}
```{r}
#| title: Knitting categories
#| padding: 4px
#| expandable: false
plot_categories()
```

### Column {width=40%}
```{r}
#| title: Knitting weights
#| padding: 4px
#| expandable: false

plot_weights()

```


# 2023
```{r}

make_value_boxes("2023")

```
## Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Completed Projects"

list(
  icon = "check-all",
  color = "secondary",
  value = completed_projects
)
```

```{r}
#| content: valuebox
#| title: "Projects started"

list(
  icon = "cone-striped",
  color = "#ffce67",
  value = started_projects
)
```

```{r}
#| content: valuebox
#| title: "Kilometers knitted"

list(
  icon = "rulers",
  color = "light",
  value = meterage |> round(digits = 2)
)
```

```{r}
#| content: valuebox
#| title: "Gifts made"

list(
  icon = "gift",
  color = "pink",
  value = gift_projects
)
```

## Row {height=70%}
### Column {width=25%}

```{r}
#| title: Most favourited project
#| padding: 0px
#| expandable: false

most_favourited <- df_year |> mutate(favorites_count = as.numeric(favorites_count)) |> filter(favorites_count == max(favorites_count)) |> slice_sample(n = 1)


images <- list.files(
    path = "data/photos/project",
    pattern = paste0(most_favourited |> select(permalink), "-\\d.jpg"),
    full.names = TRUE
)

plot <- ggplot() + geom_image(aes(x = 1,  y= 1, image = sample(images, 1)), size = 0.7) + theme_void()

table <- make_table(most_favourited)
  

plot
table
  
```


### Column {width=35%}
```{r}
#| title: Knitting categories
#| padding: 4px
#| expandable: false
plot_categories()
```

### Column {width=40%}
```{r}
#| title: Knitting weights
#| padding: 4px
#| expandable: false

plot_weights()

```



# 2022
```{r}

make_value_boxes("2022")

```
## Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Completed Projects"

list(
  icon = "check-all",
  color = "secondary",
  value = completed_projects
)
```

```{r}
#| content: valuebox
#| title: "Projects started"

list(
  icon = "cone-striped",
  color = "#ffce67",
  value = started_projects
)
```

```{r}
#| content: valuebox
#| title: "Kilometers knitted"

list(
  icon = "rulers",
  color = "light",
  value = meterage |> round(digits = 2)
)
```

```{r}
#| content: valuebox
#| title: "Gifts made"

list(
  icon = "gift",
  color = "pink",
  value = gift_projects
)
```

## Row {height=70%}
### Column {width=25%}

```{r}
#| title: Most favourited project
#| padding: 0px
#| expandable: false

most_favourited <- df_year |> mutate(favorites_count = as.numeric(favorites_count)) |> filter(favorites_count == max(favorites_count)) |> slice_sample(n = 1)


images <- list.files(
    path = "data/photos/project",
    pattern = paste0(most_favourited |> select(permalink), "-\\d.jpg"),
    full.names = TRUE
)

plot <- ggplot() + geom_image(aes(x = 1,  y= 1, image = sample(images, 1)), size = 0.7) + theme_void()

table <- make_table(most_favourited)
  

plot
table
  
```


### Column {width=35%}
```{r}
#| title: Knitting categories
#| padding: 4px
#| expandable: false

plot_categories()
```

### Column {width=40%}
```{r}
#| title: Knitting weights
#| padding: 4px
#| expandable: false

plot_weights()

```


# 2021
```{r}

make_value_boxes("2021")

```
## Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Completed Projects"

list(
  icon = "check-all",
  color = "secondary",
  value = completed_projects
)
```

```{r}
#| content: valuebox
#| title: "Projects started"

list(
  icon = "cone-striped",
  color = "#ffce67",
  value = started_projects
)
```

```{r}
#| content: valuebox
#| title: "Kilometers knitted"

list(
  icon = "rulers",
  color = "light",
  value = meterage |> round(digits = 2)
)
```

```{r}
#| content: valuebox
#| title: "Gifts made"

list(
  icon = "gift",
  color = "pink",
  value = gift_projects
)
```

## Row {height=70%}
### Column {width=25%}

```{r}
#| title: Most favourited project
#| padding: 0px
#| expandable: false

most_favourited <- df_year |> mutate(favorites_count = as.numeric(favorites_count)) |> filter(favorites_count == max(favorites_count)) |> slice_sample(n = 1)


images <- list.files(
    path = "data/photos/project",
    pattern = paste0(most_favourited |> select(permalink), "-\\d.jpg"),
    full.names = TRUE
)

plot <- ggplot() + geom_image(aes(x = 1,  y= 1, image = sample(images, 1)), size = 0.7) + theme_void()

table <- make_table(most_favourited)
  

plot
table
  
```


### Column {width=35%}
```{r}
#| title: Knitting categories
#| padding: 4px
#| expandable: false
plot_categories()
```

### Column {width=40%}
```{r}
#| title: Knitting weights
#| padding: 4px
#| expandable: false

plot_weights()

```


# 2020
```{r}

make_value_boxes("2020")

```
## Row {height="20%"}

```{r}
#| content: valuebox
#| title: "Completed Projects"

list(
  icon = "check-all",
  color = "secondary",
  value = completed_projects
)
```

```{r}
#| content: valuebox
#| title: "Projects started"

list(
  icon = "cone-striped",
  color = "#ffce67",
  value = started_projects
)
```

```{r}
#| content: valuebox
#| title: "Kilometers knitted"

list(
  icon = "rulers",
  color = "light",
  value = meterage |> round(digits = 2)
)
```

```{r}
#| content: valuebox
#| title: "Gifts made"

list(
  icon = "gift",
  color = "pink",
  value = gift_projects
)
```

## Row {height=70%}
### Column {width=25%}

```{r}
#| title: Most favourited project
#| padding: 0px
#| expandable: false

most_favourited <- df_year |> mutate(favorites_count = as.numeric(favorites_count)) |> filter(favorites_count == max(favorites_count)) |> slice_sample(n = 1)


images <- list.files(
    path = "data/photos/project",
    pattern = paste0(most_favourited |> select(permalink), "-\\d.jpg"),
    full.names = TRUE
)

plot <- ggplot() + geom_image(aes(x = 1,  y= 1, image = sample(images, 1)), size = 0.7) + theme_void()

table <- make_table(most_favourited)
  

plot
table
  
```


### Column {width=35%}
```{r}
#| title: Knitting categories
#| padding: 4px
#| expandable: false
plot_categories()
```

### Column {width=40%}
```{r}
#| title: Knitting weights
#| padding: 4px
#| expandable: false

plot_weights()

```